Gammapy: A Python package for gamma-ray astronomy

### 2023-01-27 src/ms-review.tex
review until Sect. 4

To extract physically relevant information, such as the flux, spatial or spectral shape of one or more sources,
an analytical model is commonly adopted to describe the intensity of gamma-ray sources as a function of the energy,
$E_{\rm true}$, and of the position in the field of view, $p_{\rm true}$:
$$ \Phi(p_{\rm true}, E_{\rm true}, \hat{\theta}) \quad \mathrm{[TeV^{-1}cm^{-2}s^{-1}]} $$
where $\hat{\theta}$ is a set of model parameters that can be adjusted in a fit. To convert this analytical flux model
into a prediction on the number of gamma-ray events, $N_{\rm pred}$, with their estimated energy $E$ and position $p$, the model
is convolved through the response function of the instrument.

@@

\subsection{gammapy.datasets}
\label{ssec:gammapy-datasets}
%
\begin{figure}
	\small
	\import{code-examples/generated/}{gp_datasets}
	\caption{
        Using \code{gammapy.datasets} to read existing reduced binned datasets.
        After the different datasets are read from disk they are collected into a
        common \code{Datasets} container. All dataset types have an associated
        name attribute to allow access by name later in the code. The
        environment variable \code{\$GAMMAPY\_DATA} is automtically resolved
        by \gammapy.
    }
	\label{fig*:minted:gp_datasets}
\end{figure}
%
The \code{gammapy.datasets} subpackage contains classes to bundle
together binned data along with associated models and the likelihood, which
provides an interface to the \code{Fit} class (Sec \ref{sssec:fit}) for
modeling and fitting purposes. Depending upon the type of analysis and the
associated statistic, different types of Datasets are supported. The \code{MapDataset} is
used for combined spectral and morphological (3D) fitting, and a 1D spectral fitting is
done using \code{SpectrumDataset}. While the default fit statistics for both of these
classes is the \emph{Cash}}~\citep{Cash} statistic, there are other classes which support
analyses where the background is measured from control regions, so called "off" obervations.
Those require the use of a different fit statistics, which takes into account the
uncertainty of the background measurement. This case is covered by the \code{MapDatasetOnOff}
and \code{SpectrumDatasetOnOff} classes, which use the \emph{WStat}~\citep{WStat} statistic.

@@

\subsection{gammapy.makers}
\label{ssec:gammapy-makers}
%
\begin{figure}
	\small
    \import{code-examples/generated/}{gp_makers}
	\caption{
        Using \code{gammapy.makers} to reduce DL3 level data into a
		\code{MapDataset}. All \code{Maker} classes represent 
		a step in the data reduction process. They take
        the configuration on initialisation of the class. They 
		also consistently define \code{.run()} methods, which take
		a dataset object and optionally an \code{Observation} 
		object. In this way, \code{Maker} classes can be chained
		to define more complex data reduction "pipelines".
    }
	\label{ig*:minted:gp_makers}
\end{figure}
%
The data reduction step includes all tasks required to process and prepare
\gammaray data from the DL3 level to modeling and fitting. The \code{gammapy.makers} sub-package
contains the various classes and functions required to do so. First, events are
binned and IRFs are interpolated and projected onto the chosen analysis
geometry. The end product of the data reduction process are a set of binned counts,
background exposure, psf and energy dispersion maps at the DL4 level. 
The \code{MapDatasetMaker} and \code{SpectrumDatasetMaker} are
responsible for this task, see Fig~\ref{ig*:minted:gp_makers}.

Because the background models suffer from strong uncertainties it is required
to correct them from the data themselves. Several techniques are commonly used
in TeV \gammaray astronomy such as field-of-view background normalization or
background measurement in reflected regions, see~\cite{Berge07}.
Specific \code{Makers} such as the \code{FoVBackgroundMaker} or the
\code{ReflectedRegionsBackgroundMaker} are in charge of this step.

@@

\subsection{gammapy.stats}
\label{ssec:gammapy-stats}
The \code{gammapy.stats} subpackage contains the fit statistics and associated
statistical estimators that are commonly used in \gammaray astronomy. In
general, \gammaray observations count Poisson-distributed events at various sky
positions, and contain both signal and background events. Estimation of the
number of signal events is done through likelihood maximization. In \gammapy,
the fit statistics are Poisson log-likelihood functions normalized like
chi-squares, i.e., they follow the expression $2 \time\cdot \log{\mathcal{L}}$,
where $\mathcal{L}$ is
the likelihood function used. When the expected number of background events is known, the used statistic function 
 is the \emph{Cash} statistic
~\citep{Cash}. It is used by datasets using background templates such as the
\code{MapDataset}. When the number of background events is unknown and an OFF
measurement where only background events are expected is used, the statistic
function is \emph{WStat}. It is a profile log-likelihood statistic where background
counts are marginalized parameters. It is used by datasets containing off
counts measurements such as the \code{SpectrumDatasetOnOff}, used for classical
spectral analysis.

@@

\begin{figure}
	\small
	\import{code-examples/generated/}{gp_stats}
	\caption{
        Using \code{gammapy.stats} to compute statistical quantities
        such as excess, signficance and assymetric errors
        from counts based data. The data is passed on initialisation
        of the \code{WStatCountsStatistic} class. The quantities
        are the computed ON excess of the corresponding class
        attributes such as \code{stat.n\_sig} and \code{stat.sqrt\_ts}.
    }
	\label{codeexample:stats} \end{figure}

@@

\subsubsection{Models}
\label{sssec:models}
Source models in \gammapy are four dimensional models which support two
spatial dimensions define by the sky coordinates $\ell, b$, and energy dimension $E$ as well as
the time dimension $t$. To simplify the the definition of the
models, \gammapy uses a factorised representation of the total source
model:

\begin{equation}
    f(l, b, E, t) = F(E)  \times G(l, b, E) \times  H(t, E)
\end{equation}

where the spectral model $F$ implicitly includes an \textit{amplitude} parameter
for the total flux of the model. The spatial model $G$ optionally depends
on energy and allows to support e.g. energy dependent
morphology models. The temporal model component $H$
optionally also supports an energy variable to
allow for spectral variations of the model with time.

Following the factorisation the models objects are grouped
into the following categories:
\begin{itemize}
	\item \code{SpectralModel}: models to describe spectral shapes of sources,
	\item \code{SpatialModel}: models to describe spatial shapes (morphologies) of sources,
	\item \code{TemporalModel}: models to describe temporal flux evolution of sources, such as
	      light and phase curves.
\end{itemize}

The models follow a naming scheme which contains the category as a suffix to
the class name. The spectral models include a special class of normed models,
named using the \code{NormSpectralModel} suffix.
These spectral models feature a dimension-less \textit{norm} parameter
instead of an \textit{amplitude} parameter with physical units. They
must be used along with another spectral model, as a multiplicative correction
factor according to their spectral shape. They can be typically used for
adjusting template based models, or adding taking into account
the absorbtion effect on 
\gammaray spectra caused by the extra-galactic background light (EBL) (\code{EBLAbsorptionNormSpectralModel})
model. \gammapy supports a variety of EBL absorption models, such as
\cite{Franceschini2008}, \cite{Finke2010} and \cite{Dominguez2011}.

The analytic spatial models are all normalized such as they integrate to
unity over the sky but the template spatial models may not, so in that special
case they have to be combined with a \code{NormSpectralModel}.

The \code{SkyModel} object represents factorised model that combines the spectral,
spatial and temporal model components (the spatial and temporal components being
optional). \code{SkyModel} object represents additive emission components, usually
sources or diffuse emission, although a single source can also be modeled by
multiple components. To handle list of multiple \code{SkyModel} objects, \gammapy
has a \code{Models} class.

The model gallery provides a visual overview of the available models in
\gammapy. Most of the analytic models  commonly used in \gammaray astronomy are
built-in. We also offer a wrapper to radiative models implemented in the Naima
package~\citep{naima}. The modeling framework can be easily extended with
user-defined models. For example, \agnpy models that describe leptonic radiative
processes in jetted Active Galactic Nuclei (AGN) can be wrapped into
\gammapy~\citep[see Section 3.5 of ][]{2021arXiv211214573N} .

\begin{figure}
	\small
	\import{code-examples/generated/}{gp_models}
	\caption{Using \code{gammapy.modeling.models} to define a source model with a
    spectral, spatial and temporal component. For convenience the model
    parameters can be defined as strings with attached units. The spatial model
    takes an additional \code{frame} parameter which allow users to define
    the coordinate frame of the position of the model.
    }
	\label{fig*:minted:gp_models}
\end{figure}

@@

The \code{Fit} class provides methods to fit i.e., optimise model parameters and estimate
parameter errors and correlations. It interfaces with a \code{Datasets} object, which
in turn is connected to a \code{Models} object containing the model parameters in its
\code{Parameters} object. Models can be unique for a given dataset, or contribute to
multiple datasets, allowing e.g., to do a joint fit to
multiple IACT datasets, or to a joint IACT and \fermi dataset. Many
examples are given in the tutorials.

@@

Note that, for now, covariance matrix and errors are computed only for the fitting with 
\iminuit. However depending on
the problem other optimizers can better perform, so sometimes it can be useful
to run a pre-fit with alternative optimization methods. In future we plan to
extend the supported fitting backends, including for example solutions based on Markov chain Monte Carlo methods.
\footnote{a prototype is available in gammapy-recipes,
	\url{https://gammapy.github.io/gammapy-recipes/_build/html/notebooks/mcmc-sampling-emcee/mcmc_sampling.html}
}

\subsection{gammapy.estimators}
\label{ssec:gammapy-estimators}
By fitting parametric models to the data, the total integrated
flux and overall temporal, spectral and morphological shape of the
\gammaray emission can be constrained. In many cases it is useful
to make a more detailed follow-up analysis by measuring the
flux in smaller spectral, temporal or spatial bins. This
possibly reveals more detailed emission features, which
are relevant for studying correlation with counterpart emissions.

The \code{gammapy.estimators} sub-module features methods to compute flux
points, light curves, flux maps and flux profiles from data.
The basic method for all these measurements is equivalent.
The initial fine bins of \code{MapDataset} are grouped into
larger bins. A multiplicative correction factor (the \textit{norm})
is applied to the best fit "reference" spectral
model and is fitted in the restricted data range, defined by the 
bin group, only.

In addition to the best fit flux \textit{norm} all estimators compute
quantities corresponding to this flux. This includes
the predicted number of total, signal and background
counts per flux bin. The total fit statistics
of the best fit model, the fit statistics of the
null hypothesis and the difference between both,
the so-called TS value.
From the TS value the significance of the
significance of the measured signal and associated flux
can be derived.

Optionally, it can also compute more advanced quantities
such as asymmetric flux errors, flux upper limits
and one dimensional profiles of the fit statistic,
which show how the likelihood functions varies with
the flux \textit{norm} parameter around the fit minimum.
This information is useful in inspecting the quality
of a fit, for which  a parabolic
shape of the profile is asymptomatically expected at the best fit
values.

@@

Both result objects support the possibility to serialise
the data into multiple formats. This includes the
\gadf SED format \footnote{\url{https://gamma-astro-data-formats.readthedocs.io/en/latest/spectra/flux_points/index.html}},
FITS based ND sky-maps and formats compatible with Astropy's \code{Table} and
\code{BinnedTimeSeries} data structures. This allows
users to directly further analyse the results, e.g.
standard algorithms for time analysis such as
computing Lomb-Scargle periodograms or Bayesian
blocks for time series. So far, \gammapy does not
support 'unfolding' of \gammaray spectra.
Methods for this will be implemented in a future version of \gammapy.

@@

The \code{Analysis} class has the responsibility of orchestrating of the workflow
defined in the configuration \code{AnalysisConfig} objects and triggering the execution of
the \code{AnalysisStep} classes that define the identified common use cases. These
steps include the following: observations selection with the \code{DataStore},  data
reduction, excess map computation, model fitting, flux points estimation, and
light curves production.

@@

\section{Applications}
\label{sec:applications}

\gammapy is in use for a variety of science cases by different IACT
experiments leading to more than 60 publications
\footnote{\href{https://ui.adsabs.harvard.edu/search/q=(\%20(citations(doi\%3A\%2210.1051\%2F0004-6361\%2F201834938\%22)\%20OR\%20citations(bibcode\%3A2017ICRC...35..766D))\%20AND\%20year\%3A2014-2023)&sort=date\%20desc\%2C\%20bibcode\%20desc&p_=0}{List on ADS}}.
The analysis examples shown in the following section are limited by the availability
of public data. In general, there is no limitation on performing a specific analysis
on data from a given instrument.

>>>>

To extract physically relevant information, such as the flux, spatial or spectral shape of one or more sources,
an analytical model is commonly adopted to describe the intensity of gamma-ray sources as a function of the energy,
$E_{\rm true}$, and of the position in the field of view, $p_{\rm true}$:
\begin{equation}
    \Phi(p_{\rm true}, E_{\rm true}, \hat{\theta}) \quad \mathrm{[TeV^{-1}cm^{-2}s^{-1}]}
    \label{eq:general_source_model}
\end{equation}
where $\hat{\theta}$ is a set of model parameters that can be adjusted in a fit. To convert this analytical flux model
into a prediction on the number of gamma-ray events, $N_{\rm pred}$, with their estimated energy $E$ and position $p$, the model
is convolved through the response function of the instrument.

@@

\subsection{gammapy.datasets}
\label{ssec:gammapy-datasets}
%
\begin{figure}
	\small
	\import{code-examples/generated/}{gp_datasets}
	\caption{
        Using \code{gammapy.datasets} to read existing reduced binned datasets.
        After the different datasets are read from disk they are collected into a
        common \code{Datasets} container. All dataset types have an associated
        name attribute to allow access by name later in the code. The
        environment variable \code{\$GAMMAPY\_DATA} is automtically resolved
        by \gammapy.
    }
	\label{fig*:minted:gp_datasets}
\end{figure}
%
The \code{gammapy.datasets} subpackage contains classes to bundle
together binned data along with the associated models and likelihood function, which
provides an interface to the \code{Fit} class (Sec \ref{sssec:fit}) for
modeling and fitting purposes. Depending upon the type of analysis and the
associated statistic, different types of Datasets are supported. The \code{MapDataset} is
used for combined spectral and morphological (3D) fitting, while a 1D spectral 
fitting can be performed using the \code{SpectrumDataset}.
While the default fit statistics for both of these classes is the \emph{Cash}}~\citep{Cash}
statistic, there are other classes which support
analyses where the background is measured from control regions, so called "off" obervations.
Those require the use of a different fit statistics, which takes into account the
uncertainty of the background measurement. This case is covered by the \code{MapDatasetOnOff}
and \code{SpectrumDatasetOnOff} classes, which use the \emph{WStat}~\citep{WStat} statistic.
%% CN: Wstat reference not correctly displayed in the PDF

@@

\subsection{gammapy.makers}
\label{ssec:gammapy-makers}
%
\begin{figure}
	\small
    \import{code-examples/generated/}{gp_makers}
	\caption{
        Using \code{gammapy.makers} to reduce DL3 level data into a
		\code{MapDataset}. All \code{Maker} classes represent 
		a step in the data reduction process. They take
        the configuration on initialisation of the class. They 
		also consistently define \code{.run()} methods, which take
		a dataset object and optionally an \code{Observation} 
		object. In this way, \code{Maker} classes can be chained
		to define more complex data reduction pipelines.
    }
	\label{ig*:minted:gp_makers}
\end{figure}
%
The \code{gammapy.makers} sub-package contains the various classes and functions required
to process and prepare \gammaray data from the DL3 to the DL4, representing the input for modeling and fitting.
First, events are binned and IRFs are interpolated and projected onto the chosen analysis
geometry. The end product of the data reduction process are a set of binned counts,
background exposure, psf and energy dispersion maps at the DL4 level. 
The \code{MapDatasetMaker} and \code{SpectrumDatasetMaker} are
responsible for this task for 3D and 1D analyses, respectively (see Fig~\ref{ig*:minted:gp_makers}).

Because the background models suffer from strong uncertainties it is required
to correct them from the data themselves. Several techniques are commonly used
in TeV \gammaray astronomy such as field-of-view background normalization or
background measurement in reflected regions, see~\cite{Berge07}.
Specific \code{Makers} such as the \code{FoVBackgroundMaker} or the
\code{ReflectedRegionsBackgroundMaker} are in charge of this process.
%% CN: I would add a single line explaining what each of them do

@@

\subsection{gammapy.stats}
\label{ssec:gammapy-stats}
The \code{gammapy.stats} subpackage contains the fit statistics and the associated
statistical estimators commonly adopted in \gammaray astronomy. In
general, \gammaray observations count Poisson-distributed events at various sky
positions, and contain both signal and background events. Estimation of the
number of signal events is done through likelihood maximization. In \gammapy,
the fit statistics are Poisson log-likelihood functions normalized like
chi-squares, i.e., they follow the expression $2 \time\cdot \log{\mathcal{L}}$,
where $\mathcal{L}$ is
the likelihood function used. When the expected number of background events is known, the used statistic function 
 is the \emph{Cash} statistic
~\citep{Cash}. It is used by datasets using background templates such as the
\code{MapDataset}. When the number of background events is unknown and an OFF
measurement where only background events are expected is used, the statistic
function is \emph{WStat}. It is a profile log-likelihood statistic where the background
counts are marginalized parameters. It is used by datasets containing off
counts measurements such as the \code{SpectrumDatasetOnOff}, used for classical
spectral analysis.

@@

\begin{figure}
	\small
	\import{code-examples/generated/}{gp_stats}
	\caption{
        Using \code{gammapy.stats} to compute statistical quantities
        such as excess, signficance and assymetric errors
        from counts based data. The data is passed on initialisation
        of the \code{WStatCountsStatistic} class. The quantities
        are the computed ON excess of the corresponding class
        attributes such as \code{stat.n\_sig} and \code{stat.sqrt\_ts}.
    }
	\label{codeexample:stats} \end{figure}
%% CN: the figure does not explain what alpha is

@@

\subsubsection{Models}
\label{sssec:models}
Source models in \gammapy (Eq.~\ref{eq:general_source_model}) are four-dimensional 
analytical models which support two spatial dimensions defined by the sky coordinates
$\ell, b$, an energy dimension $E$, and a time dimension $t$. To simplify the the definition of the
models, \gammapy uses a factorised representation of the total source
model:

\begin{equation}
    \phi(\ell, b, E, t) = F(E) \times G(\ell, b, E) \times H(t, E).
    \label{eq:source_model_dependency}
\end{equation}

The spectral component $F(E)$, described by the \code{SpectralModel} class, always
includes an \textit{amplitude} parameter to adjust the total flux of the model.
The spatial component $G(\ell, b, E)$, described by the \code{SpatialModel} class,
also depends on energy, in order to consider energy-dependent sources morphology.
Finally, the temporal component $H(t, E)$, described by the \code{TemporalModel}
class, also supports an energy dependency in order to consider spectral variations
of the model with time.

The models follow a naming scheme which contains the category as a suffix to
the class name. The spectral models include a special class of normed models,
named using the \code{NormSpectralModel} suffix.
These spectral models feature a dimension-less \textit{norm} parameter
instead of an \textit{amplitude} parameter with physical units. They
can be used as an energy-dependent multiplicative correction
factor to another spectral model. They are typically used for
adjusting template-based models, or, for example, to take into account
the absorbtion effect on \gammaray spectra caused by the extra-galactic background
light (EBL) (\code{EBLAbsorptionNormSpectralModel}). \gammapy supports a variety
of EBL absorption models, such as those from \cite{Franceschini2008}, \cite{Finke2010},
and \cite{Dominguez2011}.

The analytical spatial models are all normalized such as they integrate to
unity over the entire sky. The template spatial models may not, so in that special
case they have to be combined with a \code{NormSpectralModel}.

The \code{SkyModel} class represents the factorised model in Eq.~\ref{eq:source_model_dependency}
(the spatial and temporal components being optional).
A \code{SkyModel} object can represent the sum of several emission components:
either, for example, from multiple sources and from a diffuse emission, or from several spectral
components within the same source. To handle list of multiple \code{SkyModel} objects, \gammapy
implements a \code{Models} class.

%% CN: a link to the model gallery?
The model gallery provides a visual overview of the available models in
\gammapy. Most of the analytic models commonly used in \gammaray astronomy are
built-in. We also offer a wrapper to radiative models implemented in the Naima
package~\citep{naima}. The modeling framework can be easily extended with
user-defined models. For example, the radiaitve models of jetted Active Galactic Nuclei (AGN)
implemented in \agnpy, can be wrapped into \gammapy~\citep[see Section 3.5 of ][]{2022A&A...660A..18N}.

%% CN: here again, print() without output. Is it useful?
\begin{figure}
	\small
	\import{code-examples/generated/}{gp_models}
	\caption{Using \code{gammapy.modeling.models} to define a source model with a
    spectral, spatial and temporal component. For convenience the model
    parameters can be defined as strings with attached units. The spatial model
    takes an additional \code{frame} parameter which allow users to define
    the coordinate frame of the position of the model.
    }
	\label{fig*:minted:gp_models}
\end{figure}

@@

%% CN: should we mention that the dataset also include the stat function?
%% and thus the fit interfaces only with the dataset
The \code{Fit} class provides methods to fit, i.e. optimise, model parameters and estimate
their errors and correlations. It interfaces with a \code{Datasets} object, which
in turn is connected to a \code{Models} object containing the model parameters in its
\code{Parameters} object. Models can be unique for a given dataset, or contribute to
multiple datasets, allowing e.g., to perform a joint fit to
multiple IACT datasets, or to jointly fit IACT and \fermi dataset. Many
examples are given in the tutorials.
%% CN: I would write "to perform a joint fit from multiple datasets from the same instruments
%% (e.g. collected with different configurations) or from multiple datasets from different gamma-ray
%% instruments (space- and ground-based)."

@@

Note that, for now, covariance matrix and errors are computed only for the fitting with 
\iminuit. However depending on
the problem other optimizers can better perform, so sometimes it can be useful
to run a pre-fit with alternative optimization methods. In future we plan to
extend the supported fitting backends, including for example solutions based on Markov chain Monte Carlo methods.
\footnote{a prototype is available in gammapy-recipes,
	\url{https://gammapy.github.io/gammapy-recipes/_build/html/notebooks/mcmc-sampling-emcee/mcmc_sampling.html}
}
%% CN: watchout with giving links to notebooks whose position might change or disappear in the future.

\subsection{gammapy.estimators}
\label{ssec:gammapy-estimators}
By fitting parametric models to the data, the total \gammaray
flux and its overall temporal, spectral and morphological components can be constrained.
In many cases though, it is useful to make a more detailed follow-up analysis by measuring the
flux in smaller spectral, temporal or spatial bins. This
possibly reveals more detailed emission features, which
are relevant for studying correlation with counterpart emissions.

The \code{gammapy.estimators} sub-module features methods to compute flux
points, light curves, flux maps and flux profiles from data.
The basic method for all these measurements is equivalent.
The initial fine bins of \code{MapDataset} are grouped into
larger bins. A multiplicative correction factor (the \textit{norm})
is applied to the best fit "reference" spectral
model and is fitted in the restricted data range, defined by the 
bin group only.

In addition to the best-fit flux \textit{norm}, all estimators compute
quantities corresponding to this flux. This includes:
the predicted number of total, signal and background
counts per flux bin; the total fit statistics
of the best fit model; the fit statistics of the
null hypothesis; and the difference between both,
the so-called TS value.
From the TS value the significance of the measured signal and associated flux
can be derived.

Optionally, the estimators can also compute more advanced quantities
such as asymmetric flux errors, flux upper limits
and one-dimensional profiles of the fit statistic,
which show how the likelihood functions varies with
the flux \textit{norm} parameter around the fit minimum.
This information is useful in inspecting the quality
of a fit, for which a parabolic
shape of the profile is asymptomatically expected at the best fit
values.

@@

Both result objects support the possibility to serialise
the data into multiple formats. This includes the
\gadf SED format \footnote{\url{https://gamma-astro-data-formats.readthedocs.io/en/latest/spectra/flux_points/index.html}},
FITS-based ND sky maps and other formats compatible with Astropy's \code{Table} and
\code{BinnedTimeSeries} data structures. This allows
users to further analyse the results with Astropy, for example using
standard algorithms for time analysis, such as
the Lomb-Scargle periodogram or the Bayesian
blocks. So far, \gammapy does not support unfolding of \gammaray spectra.
Methods for this will be implemented in a future version of \gammapy.
%% CN: reference for unfolding https://ui.adsabs.harvard.edu/abs/2007NIMPA.583..494A/abstract

@@

The \code{Analysis} class has the responsibility of orchestrating of the workflow
defined in the configuration \code{AnalysisConfig} objects and triggering the execution of
the \code{AnalysisStep} classes that define the identified common use cases. These
steps include the following: observations selection with the \code{DataStore},  data
reduction, excess map computation, model fitting, flux points estimation, and
light curves production.
%% CN: I would not say that these are use cases, rather analysis or data reduction steps

@@

\section{Applications}
\label{sec:applications}
%% CN: I think we never explained what gammapy-data is and we should have at this point 
%% (it is used without mention also in the TSEstimator example).
\gammapy is currently used for a variety of analysis by different IACT
experiments and has already been employed in more than 60 scientific publications
\footnote{\href{https://ui.adsabs.harvard.edu/search/q=(\%20(citations(doi\%3A\%2210.1051\%2F0004-6361\%2F201834938\%22)\%20OR\%20citations(bibcode\%3A2017ICRC...35..766D))\%20AND\%20year\%3A2014-2023)&sort=date\%20desc\%2C\%20bibcode\%20desc&p_=0}{List on ADS}}.
In this section, we illustrate the capabilities of Gammapy by performing some standard
analyses cases commonly considered in gamma-ray astronomy.
The examples shown are limited by the availability of public data,
with those employed being publicly available data collected within the \code{gammapy-data} repository.
We remark that, as long as the data are compliant with the GADF specifications,
and hence with Gammapy's data structures, there is no limitation on performing
analyses of data from a given instrument.
